---
title: "Stock_Study"
output: 
  html_document:
    keep_md: true
---

##Profit vs. big report (201503)
This report is to analyze the relationship between the stock profit vs.its proportion of
shareholder whose number of stock is larger than 400 (big).


```{r setoptions,echo=FALSE,message=FALSE}
library(knitr)
library(dplyr)
opts_chunk$set(echo=TRUE)
```

```{r data}
df<-read.csv(file="D:/Stock_Study/P2.csv")
good<-complete.cases(df)
df<-df[good,]
dfs<-filter(df,big<9 & big>-10 & p>20 & profit<1)
```
#Profit vs big plot.
Based on profit and big, we separate nine regions of the stocks.
```{r profitbig,fig.height=8,fig.width=8}
with(dfs,plot(big,profit,col="blue"))
text(5,0.5,"(1)")
text(5,0.3,"(2)")
text(5,0.1,"(3)")
text(3,0.5,"(4)")
text(3,0.3,"(5)")
text(3,0.1,"(6)")
text(1,0.5,"(7)")
text(1,0.3,"(8)")
text(1,0.1,"(9)")
abline(v=0,h=0.0)
abline(v=2,h=0.2)
abline(v=4,h=0.4)
```

#Probability of each profit-big region .
In this table, we calculate the proportion of each stock region.
```{r summary}
dfs1<-dfs%>%filter(big>4 & profit>0.4)%>%arrange(desc(profit))%>%mutate(type="(1)",big_region=">4",profit_region=">40%")
dfs2<-dfs%>%filter(big>4 & profit>0.2 & profit<0.4)%>%arrange(desc(profit))%>%mutate(type="(2)",big_region=">4",profit_region="20~40%")
dfs3<-dfs%>%filter(big>4 & profit>0 & profit<0.2)%>%arrange(desc(profit))%>%mutate(type="(3)",big_region=">4",profit_region="0~20%")
dfs4<-dfs%>%filter(big>2 & big<4 & profit>0.4)%>%arrange(desc(profit))%>%mutate(type="(4)",big_region="2~4",profit_region=">40%")
dfs5<-dfs%>%filter(big>2 & big<4 & profit>0.2 & profit<0.4)%>%arrange(desc(profit))%>%mutate(type="(5)",big_region="2~4",profit_region="20~40%")
dfs6<-dfs%>%filter(big>2 & big<4 & profit>0 & profit<0.2)%>%arrange(desc(profit))%>%mutate(type="(6)",big_region="2~4",profit_region="0~20%")
dfs7<-dfs%>%filter(big>0 & big<2 & profit>0.4)%>%arrange(desc(profit))%>%mutate(type="(7)",big_region="0~2",profit_region=">40%")
dfs8<-dfs%>%filter(big>0 & big<2 & profit>0.2 & profit<0.4)%>%arrange(desc(profit))%>%mutate(type="(8)",big_region="0~2",profit_region="20~40%")
dfs9<-dfs%>%filter(big>0 & big<2 & profit>0 & profit<0.2)%>%arrange(desc(profit))%>%mutate(type="(9)",big_region="0~2",profit_region="0~20%")
dfss<-rbind(dfs1,dfs2,dfs3,dfs4,dfs5,dfs6,dfs7,dfs8,dfs9)
dfss1<-group_by(dfss,type,big_region,profit_region)
summarize(dfss1,num=length(type),prob=100*round(num/length(dfss1$type),3))
 
time<-format(Sys.time())
```

#Display the stocks in region 1~9.

Region 1 (big>4, profit>40%)
```{r display_Region1}
dfs1
```
Region 2 (big>4, profit=20~40%)
```{r display_Region2}
dfs2
```
Region 3 (big>4, profit=0~20%)
```{r display_Region3}
dfs3
```
Region 4 (big=2~4, profit>40%)
```{r display_Region4}
dfs4
```
Region 5 (big=2~4, profit=20~40%)
```{r display_Region5}
dfs5
```
Region 6 (big=2~4, profit=0~20%)
```{r display_Region6}
dfs6
```
Region 7 (big=0~2, profit>40%)
```{r display_Region7}
dfs7
```
Region 8 (big=0~2, profit=20~40%)
```{r display_Region8}
dfs8
```
Region 9 (big=0~2, profit=0~20%)
```{r display_Region9}
dfs9
```

Report time:`r time`